% ============================================================================
% DOCUMENT SETUP
% ============================================================================

\documentclass[paper=a4,fontsize=11pt]{scrartcl}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{geometry}
\textheight=700px
\usepackage{url}
\usepackage[style=iso]{datetime2}
\usepackage{atveryend}

\frenchspacing
\pagestyle{empty} 

\usepackage{sectsty}
\sectionfont{\usefont{OT1}{phv}{b}{n} \sectionrule{0pt}{0pt}{-5pt}{3pt}}

% ============================================================================
% MACROS
% ============================================================================

\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}
\newcommand{\sepspace}{\vspace*{1em}}

\newcommand{\MyName}[1]{
		\Huge \usefont{OT1}{phv}{b}{n} \hfill #1
		\par \normalsize \normalfont}
		
\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
		\noindent\hangindent=2em\hangafter=0
		\parbox{\spacebox}{\textit{#1}}
		\hspace{1.5em} #2 \par}

\newcommand{\SkillsEntry}[2]{
		\noindent\hangindent=2em\hangafter=0
		\parbox{\spacebox}{\textit{#1}}
		\hspace{1.5em} #2 \par}	
		
\newcommand{\EducationEntry}[4]{
		\noindent \textbf{#1} \hfill
		\colorbox{Black}{\parbox{6em}{\hfill\color{White}#2}} \par
		\noindent \textit{#3} \par
		\noindent\hangindent=2em\hangafter=0 \small #4
		\normalsize \par}

\newcommand{\WorkEntry}[4]{
		\noindent \textbf{#1} \hfill
		\colorbox{Black}{\color{White}#2} \par
		\noindent \textit{#3} \par
		\noindent\hangindent=1em\hangafter=0 \small #4
		\normalsize \par}
		
\newcommand{\RandomEntry}[4]{
		\noindent  \textbf{#1} \hfill
		\colorbox{Black}{\color{White}#2} \par
		\noindent \textit{#3} \par
		\noindent\hangindent=0em\hangafter=0 \small #4
		\normalsize \par}

\newcommand{\Metadata}[1]{
		\tiny \usefont{OT1}{phv}{m}{n} \hfill #1
		\par \normalsize \normalfont}

% ============================================================================
% DOCUMENT
% ============================================================================

\begin{document}

\Metadata{Last Updated: \today}
\Metadata{GitHub Commit: verSubstitution}

\MyName{Dominic Bean}

% ============================================================================
% PERSONAL DETAILS
% ============================================================================

\NewPart{Personal Details}{}

\PersonalEntry{Nationality}{British}
\PersonalEntry{Languages}{English \& Thai (conversational)}

% ============================================================================
% SKILLS & TOOLS
% ============================================================================

\NewPart{Skills \& Tools}{}
\SkillsEntry{Software}{R, Python, \LaTeX, \text{Git}, SQL, Bash, Vim, Microsoft Excel, AWS}
\SkillsEntry{Portfolio}{\url{https://dombean.com}}

% ============================================================================
% EDUCATION
% ============================================================================

\NewPart{Education}{}

\EducationEntry
{MSc Data Science | with Merit}
{2018 - 2019}{University of Lancaster | Departmental Scholarship Award |  Business Intelligence Pathway}
{\textbullet\ Modules: Data Science Fundamentals, Data Mining, Statistical Inference, Statistical Methods and Modelling, Programming for Data Scientists, Introduction to Intelligent Data Analysis, Statistical Learning, Optimisation and Heuristics, Forecasting.}

\sepspace

\EducationEntry
{BSc Economics | First Class Honours}
{2015 - 2018}{Manchester Metropolitan University}
{\textbullet\ Final Year Modules: Advanced Economic Theory (Macroeconomics and Microeconomics), Econometrics: Analysis and Forecasting, Corporate Finance and Investments Analysis, Quantitative Dissertation.}

\sepspace

\EducationEntry
{International Baccalaureate Diploma}
{2012 - 2014}{Discovery College, Hong Kong}
{\textbullet\ UCAS Points: 378 (Old Tariff - Pre 2017) \newline 
\textbullet\ Subjects Taken: Economics, Business and Management, Design Technology, Maths Studies, English Language and Literature, Spanish Ab Inito.}

% ============================================================================
% PROJECTS
% ============================================================================

\NewPart{Projects}{}

\RandomEntry{Master's Dissertation: Credit Risk Classification}{2019}{}
{Analysed the performance of six classification algorithms on \textit{Lending Club} Data, a peer-to-peer lending company. Lending Club, one of the biggest P2P companies in the United States, regularly releases anonymised datasets of their customers containing numerous features related to the characteristics of a loan and the borrower. This information can be used to classify whether or not a borrower will default on their loan. My thesis explored Lending Club's data collected over the years: 2007 to 2018, which contained in excess of 2 million observations and more than 150 variables.\\

\noindent The hyperparameters of the various classification models were tuned and evaluated using Grid/Random Grid Search alongside K-Fold Cross-Validation -- the best model/s were determined using the ROC-AUC metric. Furthermore, as the dependent variable was imbalanced; random oversampling and random undersampling methods were also investigated to determine if the predictive performance of the classifiers could be improved using such methods.}

\sepspace

\RandomEntry{Undergraduate Corporate Finance Coursework}{2018}{}{Used discounted cash flows and other financial valuation techniques to value companies and securities. After, I devised a basic trading strategy, implemented it in Python, and back-tested it against financial data.}

% ============================================================================
% WORK EXPERIENCE
% ============================================================================

\NewPart{Work Experience}{}

\WorkEntry{Graduate Data Scientist}
{March 2020 - October 2020}
{Jet2}
{\textbullet\ Used Google BigQuery to ingest data provided by the business. Started working on clustering web-site visitors using scikit-learn (and other packages).}

\sepspace

\WorkEntry{Course Representative, Peer Mentor, IT Rover}
{2015 - 2018}
{Manchester Metropolitan University, Part-Time}
{\textbullet\ Course Representative: conveying the concerns of my peers in a clear and persuasive manner to my lecturers. \newline 
\textbullet\ Peer Mentor: responsibilities included teaching students, meeting and greeting prospective students and their parents, helping staff out with student interviews. \newline 
\textbullet\ IT Rover: helping students and staff with general IT issues, as well as maintaining printers and other computer equipment.}

\sepspace

\WorkEntry
{Officer Cadet}
{2015 - 2016}
{Manchester and Salford Royal Navy Universities Unit}
{\textbullet\ Opportunity to serve as an officer cadet and sail on a Royal Navy ship, where my role was primarily as an “Engineer”. Others roles included navigation, radar work, and more.}

\end{document}
